Python as a machine learning language: experiences from the \textit{scikit-learn} project

### 2013-06-08 paper.tex
todos
TODOs

\textcolor{red}{TODO: Focus on the experience we accumulated (general remark); motivate our design choices.}

@@

As the above snippet shows, \texttt{Pipeline} and \texttt{FeatureUninon}
can be combined to create complex objects. In particular, since both
are themselves estimators, they can be used to form nested workflows.

@@

@@

@@

>>>>

\noindent \textcolor{red}{TODO: Focus on the experience we accumulated (general remark)}\\
\textcolor{red}{TODO: Motivate our design choices.}

@@

As the above snippet shows, \texttt{Pipeline} and \texttt{FeatureUninon} can be
combined to create complex objects. In particular, since both are themselves
estimators, they can be used to form nested workflows. \textcolor{red}{TODO:
elaborate a bit more on nested constructions.}

@@

\noindent \textcolor{red}{TODO: Mention small set of dependencies.}\\
\textcolor{red}{TODO: elaborate on use of mixins and duck typing}

@@

\textcolor{red}{TODO: move this into the Implementation section? These are mostly implementation considerations.}

@@

\textcolor{red}{TODO: compare with weka, R, vowpal rabbit, ... ?}\\
\textcolor{red}{TODO: emphasize scikit-learn's place in the overall scipy ecosystem, and its role in spurring the development of more basic tools.}\\
\textcolor{red}{TODO: some packages start to adopt our own API.}
